Response to reviewers

### 2022-02-18 paper/paper.Rmd
Corrects the spelling and grammatical in Section 4.2 and 4.3.

For `gender` and `race`, we only rename the column names provided in the raw data, `new_data_qnames`. It is worth noting that `gender` comes from a variable called `sex` in the database. We use the term `gender` as the reports about the data on various pages in the website more commonly use `gender`. Gender, as provided in the data, is self-reported and only has two categories, "male" and "female". The interchangeable use of these terms reflects that gender and sex are sometimes regarded as similar in surveys, although they are not. Measuring gender as a binary variable has the potential to fail to capture people who do not identify themselves as either male or female or people whose gender does not align with their sex classification [@kennedy2020using]. From a statistical perspective, this sometimes difficult the adjustment of survey statistics to the population when gender is measured, for example, with three categories, and the census measured it with only two categories and used the term sex [@kennedy2020using]. Hence, for modern societal studies, it is highly recommended to separate sex and gender in the survey question and provide more options to respond to questions on gender. This discourse should also be emphasized in teaching that using these two variables should be accompanied by special attention. Similar this also relates to race, as reported in the database. When doing an analysis with this variable, one should keep in mind that the purpose is to study racism rather than race.

@@

Because the original data does not have the year of collection, it is not possible to directly merge the two subsets. Merging longitudinal data requires both the key (`id`) and the index (ideally survey year). In the original data the experience variable is the time index, and it was not possible to exactly match this for the refreshed data. Thus, comparisons of the two sets has to be conducted in a two sample fashion rather than as a matched sample.

Figure \ref{fig:compare-subsets} contains summaries of corresponding variables in the two subsets. Plot (A) shows a back-back bar chart of the highest grade completed. The two sets are almost the same, but small differences remain. Plots (B) and (C) show stacked density plots of experience and log wages, respectively. The distributions are relatively close, with more differences in wages as would be expected becuase the refreshed data is not inflation-adjusted.

@@

There are several aspects of the original data that were difficult to replicate. Calculation of the work experience is not clearly articulated. @SingerJudithD2003Alda describe the temporal variable as the years of experience since the first day of work. This variable is not explicitly available in the database. From the NLSY79 topical guide [@nlsy79guide], we find that several variables are tagged as work experience-related variables. One of them is the weeks of worked since the last interview. This is used to calculate the variable. It produces reasonably similar but not exactly the same values. Because the original data set did not include year of the survey, it cannot be precisely compared.

Highest grade completed has some confusion. There are several ways that this is reported, including the highest grade ever completed, and also the hgc at each survey year. To match the original data, it is appropriate to use the hgc while in high school. The documentation suggests that this variable is available but it is not actually present in the data. Hence, for matching the original data, we have calculated the hgc to match the hgc achieved in the years between 1979 and 1994 based on the yearly survey value. The result does not exactly match with the original for a few individuals.

In the original dataset, wages were inflation-adjusted to 1990 prices. This is not done for the refreshed data because we plan to keep refreshing it as the data added to and released from the survey. Instead we have provided a function in the R package, `r yowie`, for users to conduct the inflation adjustment when they are ready to analyse the data.

<!--AE comment: “The treatment of unlikely wages differ in the refreshed data.” I think this means “The treatment of anomalous wages differs between the original and refreshed data sets.” Then you say “We opted to use the weights from a robust linear regression to determine what should be set as missing value as described in Section 3.2.1.” I don’t think you were setting missing values though, were you? It was used to determine which values should be imputed, correct? Either way, please clarify.-->
It is important to note that the treatment of unlikely wages differs in the refreshed data. In the original data by @SingerJudithD2003Alda, wages greater than $75 are set to be missing. However, this value is too low to be set as the maximum threshold, and it doesn't take into account temporal neighbors for an individual. We opted to use the weights from a robust linear regression to determine what should be regarded as extreme and imputed them with their predicted values as as described in Section \@ref(censor).

Lastly, the race variable is almost perfectly matched. The id's in the dropouts subset of the refreshed data all correspond to males, which is a perfect match with the original subset.

>>>>

For `gender` and `race`, we only rename the column names provided in the raw data, `new_data_qnames`. It is worth noting that `gender` comes from a variable called `sex` in the database. We use the term `gender` as the reports about the data on various pages in the website more commonly use `gender`. Gender, as provided in the data, is self-reported and only has two categories, "male" and "female". The interchangeable use of these terms reflects that gender and sex are sometimes regarded as similar in surveys, although they are not. Measuring gender as a binary variable has the potential to fail to capture people who do not identify themselves as either male or female or people whose gender does not align with their sex classification [@kennedy2020using]. From a statistical perspective, this sometimes difficult the adjustment of survey statistics to the population when gender is measured, for example, with three categories, and the census measured it with only two categories and used the term sex [@kennedy2020using]. Hence, for modern societal studies, it is highly recommended to separate sex and gender in the survey question and provide more options to respond to questions on gender. This discourse should also be emphasized in teaching that using these two variables should be accompanied by special attention. Similarly, this also relates to race, as reported in the database. When doing an analysis with this variable, one should keep in mind that the purpose is to study racism rather than race.

@@

Because the original data does not have the year of collection, it is not possible to merge the two subsets directly. Merging longitudinal data requires both the key (`id`) and the index (ideally survey year). In the original data, the experience variable is the time index, and it was not possible to exactly match this for the refreshed data. Thus, comparisons of the two sets have to be conducted in a two-sample fashion rather than a matched sample.

Figure \ref{fig:compare-subsets} contains summaries of corresponding variables in the two subsets. Plot (A) shows a back-back bar chart of the highest grade completed. The two sets are almost the same, but small differences remain. Plots (B) and (C) show stacked density plots of experience and log wages, respectively. The distributions are relatively close, with more differences in wages as would be expected because the refreshed data is not inflation-adjusted.

@@

There are several aspects of the original data that were difficult to replicate. The calculation of the work experience is not clearly articulated. @SingerJudithD2003Alda describe the temporal variable as the years of experience since the first day of work. This variable is not explicitly available in the database. From the NLSY79 topical guide [@nlsy79guide], we find that several variables are tagged as work experience-related variables. One of them is the weeks of worked since the last interview. This is used to calculate the variable. It produces reasonably similar but not exactly the same values. Because the original data set did not include the year of the survey, it cannot be precisely compared.

The highest grade completed has some confusion. There are several ways that this is reported, including the highest grade ever completed and also the `hgc` at each survey year. To match the original data, it is appropriate to use the `hgc` while in high school. The documentation suggests that this variable is available, but it is not actually present in the data. Hence, for matching the original data, we have calculated the `hgc` to match the `hgc` achieved in the years between 1979 and 1994 based on the yearly survey value. The result does not exactly match with the original for a few individuals.

In the original dataset, wages were inflation-adjusted to 1990 prices. This is not done for the refreshed data because we plan to keep refreshing it as the data is added to and released from the survey. Instead, we have provided a function in the R package, `r yowie`, for users to conduct the inflation adjustment when they are ready to analyse the data.

<!--AE comment: “The treatment of unlikely wages differ in the refreshed data.” I think this means “The treatment of anomalous wages differs between the original and refreshed data sets.” Then you say “We opted to use the weights from a robust linear regression to determine what should be set as missing value as described in Section 3.2.1.” I don’t think you were setting missing values though, were you? It was used to determine which values should be imputed, correct? Either way, please clarify.-->
It is important to note that the treatment of unlikely wages differs in the refreshed data. In the original data by @SingerJudithD2003Alda, wages greater than $75 are set to be missing. However, this value is too low to be set as the maximum threshold, and it doesn't take into account temporal neighbors for an individual. We opted to use the weights from a robust linear regression to determine what should be regarded as extreme and imputed them with their predicted values as described in Section \@ref(censor).

Lastly, the race variable is almost perfectly matched. The `id`'s in the dropouts subset of the refreshed data all correspond to males, which perfectly matches the original subset.

### 2022-02-18 paper/paper.tex
Corrects the spelling and grammatical in Section 4.2 and 4.3.

For \texttt{gender} and \texttt{race}, we only rename the column names provided in the raw data, \texttt{new\_data\_qnames}. It is worth noting that \texttt{gender} comes from a variable called \texttt{sex} in the database. We use the term \texttt{gender} as the reports about the data on various pages in the website more commonly use \texttt{gender}. Gender, as provided in the data, is self-reported and only has two categories, ``male'' and ``female''. The interchangeable use of these terms reflects that gender and sex are sometimes regarded as similar in surveys, although they are not. Measuring gender as a binary variable has the potential to fail to capture people who do not identify themselves as either male or female or people whose gender does not align with their sex classification (Kennedy et al. 2020). From a statistical perspective, this sometimes difficult the adjustment of survey statistics to the population when gender is measured, for example, with three categories, and the census measured it with only two categories and used the term sex (Kennedy et al. 2020). Hence, for modern societal studies, it is highly recommended to separate sex and gender in the survey question and provide more options to respond to questions on gender. This discourse should also be emphasized in teaching that using these two variables should be accompanied by special attention. Similar this also relates to race, as reported in the database. When doing an analysis with this variable, one should keep in mind that the purpose is to study racism rather than race.

@@

Because the original data does not have the year of collection, it is not possible to directly merge the two subsets. Merging longitudinal data requires both the key (\texttt{id}) and the index (ideally survey year). In the original data the experience variable is the time index, and it was not possible to exactly match this for the refreshed data. Thus, comparisons of the two sets has to be conducted in a two sample fashion rather than as a matched sample.

Figure \ref{fig:compare-subsets} contains summaries of corresponding variables in the two subsets. Plot (A) shows a back-back bar chart of the highest grade completed. The two sets are almost the same, but small differences remain. Plots (B) and (C) show stacked density plots of experience and log wages, respectively. The distributions are relatively close, with more differences in wages as would be expected becuase the refreshed data is not inflation-adjusted.

@@

There are several aspects of the original data that were difficult to replicate. Calculation of the work experience is not clearly articulated. Singer and Willett (2003) describe the temporal variable as the years of experience since the first day of work. This variable is not explicitly available in the database. From the NLSY79 topical guide (Bureau of Labor Statistics, U.S. Department of Labor 2021b), we find that several variables are tagged as work experience-related variables. One of them is the weeks of worked since the last interview. This is used to calculate the variable. It produces reasonably similar but not exactly the same values. Because the original data set did not include year of the survey, it cannot be precisely compared.

Highest grade completed has some confusion. There are several ways that this is reported, including the highest grade ever completed, and also the hgc at each survey year. To match the original data, it is appropriate to use the hgc while in high school. The documentation suggests that this variable is available but it is not actually present in the data. Hence, for matching the original data, we have calculated the hgc to match the hgc achieved in the years between 1979 and 1994 based on the yearly survey value. The result does not exactly match with the original for a few individuals.

In the original dataset, wages were inflation-adjusted to 1990 prices. This is not done for the refreshed data because we plan to keep refreshing it as the data added to and released from the survey. Instead we have provided a function in the R package, \texttt{[CENSORED]}, for users to conduct the inflation adjustment when they are ready to analyse the data.

It is important to note that the treatment of unlikely wages differs in the refreshed data. In the original data by Singer and Willett (2003), wages greater than \$75 are set to be missing. However, this value is too low to be set as the maximum threshold, and it doesn't take into account temporal neighbors for an individual. We opted to use the weights from a robust linear regression to determine what should be regarded as extreme and imputed them with their predicted values as as described in Section \ref{censor}.

Lastly, the race variable is almost perfectly matched. The id's in the dropouts subset of the refreshed data all correspond to males, which is a perfect match with the original subset.

>>>>

For \texttt{gender} and \texttt{race}, we only rename the column names provided in the raw data, \texttt{new\_data\_qnames}. It is worth noting that \texttt{gender} comes from a variable called \texttt{sex} in the database. We use the term \texttt{gender} as the reports about the data on various pages in the website more commonly use \texttt{gender}. Gender, as provided in the data, is self-reported and only has two categories, ``male'' and ``female''. The interchangeable use of these terms reflects that gender and sex are sometimes regarded as similar in surveys, although they are not. Measuring gender as a binary variable has the potential to fail to capture people who do not identify themselves as either male or female or people whose gender does not align with their sex classification (Kennedy et al. 2020). From a statistical perspective, this sometimes difficult the adjustment of survey statistics to the population when gender is measured, for example, with three categories, and the census measured it with only two categories and used the term sex (Kennedy et al. 2020). Hence, for modern societal studies, it is highly recommended to separate sex and gender in the survey question and provide more options to respond to questions on gender. This discourse should also be emphasized in teaching that using these two variables should be accompanied by special attention. Similarly, this also relates to race, as reported in the database. When doing an analysis with this variable, one should keep in mind that the purpose is to study racism rather than race.

@@

Because the original data does not have the year of collection, it is not possible to merge the two subsets directly. Merging longitudinal data requires both the key (\texttt{id}) and the index (ideally survey year). In the original data, the experience variable is the time index, and it was not possible to exactly match this for the refreshed data. Thus, comparisons of the two sets have to be conducted in a two-sample fashion rather than a matched sample.

Figure \ref{fig:compare-subsets} contains summaries of corresponding variables in the two subsets. Plot (A) shows a back-back bar chart of the highest grade completed. The two sets are almost the same, but small differences remain. Plots (B) and (C) show stacked density plots of experience and log wages, respectively. The distributions are relatively close, with more differences in wages as would be expected because the refreshed data is not inflation-adjusted.

@@

There are several aspects of the original data that were difficult to replicate. The calculation of the work experience is not clearly articulated. Singer and Willett (2003) describe the temporal variable as the years of experience since the first day of work. This variable is not explicitly available in the database. From the NLSY79 topical guide (Bureau of Labor Statistics, U.S. Department of Labor 2021b), we find that several variables are tagged as work experience-related variables. One of them is the weeks of worked since the last interview. This is used to calculate the variable. It produces reasonably similar but not exactly the same values. Because the original data set did not include the year of the survey, it cannot be precisely compared.

The highest grade completed has some confusion. There are several ways that this is reported, including the highest grade ever completed and also the \texttt{hgc} at each survey year. To match the original data, it is appropriate to use the \texttt{hgc} while in high school. The documentation suggests that this variable is available, but it is not actually present in the data. Hence, for matching the original data, we have calculated the \texttt{hgc} to match the \texttt{hgc} achieved in the years between 1979 and 1994 based on the yearly survey value. The result does not exactly match with the original for a few individuals.

In the original dataset, wages were inflation-adjusted to 1990 prices. This is not done for the refreshed data because we plan to keep refreshing it as the data is added to and released from the survey. Instead, we have provided a function in the R package, \texttt{[CENSORED]}, for users to conduct the inflation adjustment when they are ready to analyse the data.

It is important to note that the treatment of unlikely wages differs in the refreshed data. In the original data by Singer and Willett (2003), wages greater than \$75 are set to be missing. However, this value is too low to be set as the maximum threshold, and it doesn't take into account temporal neighbors for an individual. We opted to use the weights from a robust linear regression to determine what should be regarded as extreme and imputed them with their predicted values as described in Section \ref{censor}.

Lastly, the race variable is almost perfectly matched. The \texttt{id}'s in the dropouts subset of the refreshed data all correspond to males, which perfectly matches the original subset.

### 2022-02-18 response/response1.Rmd
Corrects the spelling and grammatical in Section 4.2 and 4.3.

\begin{description}
\item[Reviewer 3:]\textcolor{violet}{The authors explain the complication of the “years of job experience” variable being unavailable in the raw data. This information is available in the NLSY79 data accessor; it seems to simply have been not selected in the initial data download by the authors.
Given that the stated goal is to recreate the textbook data, this seems like a glaring oversight.
It also leads to Fig 7 (Now Figure 8) being essentially meaningless: we are unsurprised that salaries are higher with more years of experience, and we are unsurprised that salaries go up over the years with both age of employee and inflation. The positive slope of these two different plots does not mean they are related to each other in any way.}
\end{description}

@@

* Sometimes, the natural log is used to rescale the variable in the graph to adjust with the skewness in the data. Singer and Willet (2003) use the natural log to store the wages data by default, although without mention their motivation of doing so. Thus, we also use the natural log in Figure 8 to compare the refreshed data with the original data.

@@

* We have changed Fig 2 to show 36 individuals, that display the range of wages experience, including some with questionable values. The figure caption reflects this and more details are provide din the text.

>>>>

\begin{description}
\item[Reviewer 3:]\textcolor{violet}{The authors explain the complication of the “years of job experience” variable being unavailable in the raw data. This information is available in the NLSY79 data accessor; it seems to simply have been not selected in the initial data download by the authors.
Given that the stated goal is to recreate the textbook data, this seems like a glaring oversight.
It also leads to Fig 7 being essentially meaningless: we are unsurprised that salaries are higher with more years of experience, and we are unsurprised that salaries go up over the years with both age of employee and inflation. The positive slope of these two different plots does not mean they are related to each other in any way.}
\end{description}

@@

* Sometimes, the natural log is used to rescale the variable in the graph to adjust with the skewness in the data. Singer and Willet (2003) use the natural log to store the wages data by default, although without mention their motivation of doing so. Thus, we also use the natural log in Figure 7 to compare the refreshed data with the original data.

@@

* We have changed Fig 2 to show 36 individuals, that display the range of wages experience, including some with questionable values. The figure caption reflects this and more details are provided in the text.
